Predictive modeling with cross validation

### 2017-08-17 model fitting/cross_validation.Rmd
updated lit file

  # returns a list containing performance metrics, and data frame with predicted survival probabilities
  output <- list(metrics, probs)
  return(output)
}

```

>>>>

  # returns a list containing performance metrics, and data frame with predicted survival probabilities
  output <- list(metrics, probs)
  return(output)
}
```
